Real-time epidemiological estimates from ONS Community Infection Survey data

### 2022-03-02 docs/report.Rmd
add horizons
text tweaks

quantities <- c(est_prev = "PCR+ prevalence",
                infections = "Infection incidence",
                r = "Growth rate",
                Rt = "Reproduction number",
                cumulative_infections = "Cumulative incidence",
                cumulative_exposure = "Proportion ever infected")

time_horizon <- c(est_prev = "1year",
                  infections = "1year",
                  r = "3months",
                  Rt = "3months")

@@

```{r, results = 'asis', echo = FALSE}
for (level in names(estimates)) {
  cat("\n\n#", estimates[[level]], "estimates", "{.tabset}", "\n")
  for (quantity in names(quantities)) {
    cat("\n\n##", quantities[[quantity]], "\n")
    cat(additional_text[[quantity]], "\n")
    file_name <-
      paste0(level, "_", quantity, "_", time_horizon[[quantity]], ".png")
    p <- ggdraw() + draw_image(here::here("figures", "additional", file_name))
    print(p)
  }
}
```

>>>>

quantities <- c(est_prev = "PCR+ prevalence",
                infections = "Infection incidence",
                r = "Growth rate",
                Rt = "R",
                cumulative_infections = "Cumulative incidence",
                cumulative_exposure = "Proportion ever infected")

time_horizon <- c(est_prev = "1year",
                  infections = "1year",
                  r = "3months",
                  Rt = "3months",
                  cumulative_infections = "1year",
                  cumulative_exposure = "1year")

@@

```{r, results = 'asis', echo = FALSE}
for (level in names(estimates)) {
  cat("\n\n#", estimates[[level]], "estimates", "{.tabset}", "\n")
  for (quantity in names(quantities)) {
    cat("\n\n##", quantities[[quantity]], "\n")
    cat(additional_text[[quantity]], "\n\n")
    file_name <-
      paste0(level, "_", quantity, "_", time_horizon[[quantity]], ".png")
    p <- ggdraw() + draw_image(here::here("figures", "additional", file_name))
    print(p)
  }
}
```
